---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# statskier2

This package is a collection of functions I use to explore and analyze cross-
country skiing results data that I have collected over the years. The data itself
is not included in the package, so the this package isn't actually functional
on its own.

## Examples

Some basic plots of results by skier:

```{r ath-plots,warning=FALSE}
library(statskier2)
p <- ath_plot_dst(ath_names = c("WENG Heidi","SOMMERFELDT Rene","BJOERGEN Marit"))
print(p$plot)

p <- ath_plot_spr(ath_name = c("NEWELL Andrew","RANDALL Kikkan"))
print(p$plot)

p <- spr_plot(ath_names = c('NEWELL Andrew','HAMILTON Simeon'))
print(p$plot)
```

Some head-to-head plots:

```{r ath-hth}
p <- hth_race(ath_name = 'DIGGINS Jessica',race_id = 9232,num_opp = 30,min_encounters = 3,measure = 'pb')
print(p$plot)

p <- hth_lmer(ath_names = 'DIGGINS Jessica',race_id = 9232,num_opp = 30,min_encounters = 3,measure = 'pb')
print(p$plot)
```

Results trends by nation:

```{r nation-trend}
p <- nation_trend(nations = c('USA','CAN','RUS','SWE'),
                  race_gender = 'Men',
                  race_type = 'Distance')
print(p$plot)
```

Individual race snapshots:

```{r race-snapshot}
p <- race_snapshot_dst(race_id = 7902,title = "Men's 15k Classic - 2014-11-30")
print(p$plot)
```

World Junior & U23 results over time by nation:

```{r wjc-u23}
p <- wjc_u23_plot(nations = c('USA','CAN'),races = 'WJC')
print(p$plots$USA)
print(p$plots$CAN)
```
